Decisions Decisions Decisions: Carrying out Latent Profile Analysis in Accordance With Best Practices Using the tidyLPA R package

### 2020-08-27 paper.rmd
update

````{r, compare-mclust}
compare_solutions_mclust <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9,
                    package = "mclust")
```

```{r, eval = FALSE}
write_rds(compare_solutions_mclust, "compare_solutions_mclust.rds")
````

```{r, compare-mplus}
compare_solutions_mplus <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 4, 5, 6),
                    n_profiles = 1:9,
                    package = "mplus")
```

```{r, echo = FALSE}
write_rds(compare_solutions_mplus, "compare_solutions_mplus.rds")
```

```{r, compare-mplus-starts}
compare_solutions_mplus_starts <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 4, 5, 6),
                    n_profiles = 1:9,
                    package = "mplus",
                    ANALYSIS = "starts = 100, 20;")
```

```{r, echo = FALSE}
write_rds(compare_solutions_mplus_starts, "compare_solutions_mplus_starts.rds")
```

>>>>

````{r, compare-mclust, eval= FALSE}
compare_solutions_mclust <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9,
                    package = "mclust")
```

```{r, eval = FALSE, echo = FALSE}
write_rds(compare_solutions_mclust, "compare_solutions_mclust.rds")
```

```{r, echo = FALSE}
compare_solutions_mclust <- read_rds("compare_solutions_mclust.rds")
compare_solutions_mclust
```

```{r, compare-mplus, eval = FALSE}
compare_solutions_mplus <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 4, 5, 6),
                    n_profiles = 1:9,
                    package = "mplus")
```

```{r, echo = FALSE, eval = FALSE}
write_rds(compare_solutions_mplus, "compare_solutions_mplus.rds")
```

```{r, echo = FALSE}
compare_solutions_mplus <- read_rds("compare_solutions_mplus.rds")
compare_solutions_mplus
```

```{r, compare-mplus-starts, eval = FALSE}
compare_solutions_mplus_starts <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 4, 5, 6),
                    n_profiles = 1:9,
                    package = "mplus",
                    ANALYSIS = "starts = 100, 20;")
```

```{r, echo = FALSE, eval = FALSE}
write_rds(compare_solutions_mplus_starts, "compare_solutions_mplus_starts.rds")
```

```{r, echo = FALSE}
compare_solutions_mplus <- read_rds("compare_solutions_mplus_starts.rds")
compare_solutions_mplus
```
